sensiAnPaper1All

### 2017-12-13 inst/documents/sensiAnPaper1All.Rmd
tidy

### All code for the sensitivity analysis for the first paper

@@

  #2) mixture1 : time to resistance for either insecticide when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for EITHER insecticide in mixture  
  resistPointsMix_1 <- findResistancePoints(listOutMix, locus='either')  
  #todo - to be comparable I think this should be for when resistance to BOTH insecticides is reached

>>>>

### code to start the sensitivity analysis for the first paper
### main analyses of results is in : paper1_results_figs_slimmed_50_rr

@@

  #2) mixture1 : time to resistance for either insecticide when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for EITHER insecticide in mixture  
  resistPointsMix_1 <- findResistancePoints(listOutMix, locus='either')
